%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ritik}{Kumar}{ % Your name profile or other web address
\href{https://ritik.ml}{\bf Portfolio} 
\href{https://github.com/dev-ritik}{\bf GitHub} 
\href{https://www.linkedin.com/in/ritik-kumar/}{\bf LinkedIn}
\href{https://medium.com/@ritikk}{\bf Medium} \\
\href{mailto:ritikkne@gmail.com}{ritikkne@gmail.com} | \href{mailto:rkumar1@cs.iitr.ac.in}{rkumar1@cs.iitr.ac.in}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Summary}
Back end and DevOps programmer interested in Computer Networks \& Protocols, Cloud and Distributed Computing. Open Source contributor.
\sectionspace % Some white space after the section

\section{Skills}
\subsection{LANGUAGES}
\subsubsection*{Comfortable}
\squeezeup
Python, Java, Go, JavaScript, TypeScript, HTML/CSS, Markdown, bash
\subsectionspace % Some white space after the subsection
\subsubsection*{Familiar}
\squeezeup
Kotlin, C, C++, C\#, Q\#, C, CoffeeScript

\sectionspace % Some white space after the section

\subsection{FRAMEWORKS/LIBRARIES}
\subsubsection*{Comfortable}
\squeezeup
AWS Boto, Django, Android Java Framework, Bee (Go)
\subsectionspace % Some white space after the subsection
\subsubsection*{Familiar}
\squeezeup
.NET

\sectionspace % Some white space after the section

\subsection{SOFTWARE/TOOLS/SERVICES}
Git \& GitHub, CI (Circle), Sentry \\
Vim, Sublime Text, VScode, JetBrains IDEs \\
make, Doxygen, ssh, Nginx, Docker, Docker-compose \\
MongoDB, PostgreSQL, Redis Cache, Elastic Search \\
Mininet, Wireshark, Tcpdump \\
Heroku, Firebase-GCP, AWS \\
GNU/Linux 20.04.1 LTS, Windows 10 Home


\sectionspace % Some white space after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

%------------------------------------------------

\subsection{B. Tech., COMPUTER SCI. AND Engg. }
\descript{CGPA 8.216}
\location{Indian Institute of Technology, Roorkee, India (2021)}

\sectionspace % Some white space after the section

\subsection{Senior Secondary Education}
\descript{Boards 92\%}
%\location{Bal Mandir Senior Secondary School, Kishanganj}


%------------------------------------------------
% Links
%------------------------------------------------

% \section{Links} 

% GitHub:// \href{https://github.com/dev-ritik}{\bf dev-ritik} \\
% LinkedIn:// \href{https://www.linkedin.com/in/ritik-kumar}{\bf ritik-kumar} \\
% Twitter:// \href{https://twitter.com/ritik___}{\bf @ritik___} \\

%------------------------------------------------
% Volunteer
%------------------------------------------------

\section{Responsibility} 
\sectionspace % Some white space after the section
\begin{tightitemize}
\item Back-end \& Systems Developer and Mentor \href{https://mdg.iitr.ac.in}{\bf @MDG IIT Roorkee}.
\item Product Manager \href{https://mess.iitr.ac.in}{\bf @Appetizer}.
\item Volunteer \href{https://www.iitr.ac.in/nss/}{\bf @NSS IIT Roorkee}.
\end{tightitemize}

% \sectionspace % Some white space after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{MICROSOFT EDGE}
\descript{| Software Developer Remote Intern}

\location{Microsoft 2020}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed a new feature to share EDGE Collections.
\item Set up the service to share the Collection and looked into syncing them.
\item Modified the Edge's codebase to modify and expose the API.
\end{tightitemize}

\sectionspace % Some white space after the section

\runsubsection{Google Summer of Code}
\descript{| Student Developer |  \href{https://github.com/named-data-mobile/ndn-photo-app}{Link}}
\location{Named Data Network 2019}
\begin{tightitemize}
\item Developed NpChat, a photo and ﬁle-sharing peer-to-peer decentralised application built on Android on NDN (ICN). Access control is ensured using encryption and data is fetched using AIMD pipelined Segment-Fetcher.
\item Wrote the AIMD pipelined Segment-Fetcher for their Java Support Library.
\item Updated the user Identity management application for NpChat.
\end{tightitemize}

\sectionspace % Some white space after the section

\runsubsection{Blogs}
\descript{| Technical Writer |  \href{https://medium.com/@ritikk}{Link}}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
Wrote a number of blogs on Computer Networks and Protocols.


\sectionspace % Some whitespace after the section
%------------------------------------------------

% Project
%------------------------------------------------

\section{Projects} 

\runsubsection{Appetizer}
\descript{| Product Manager \& Back end Head | \href{https://mess.iitr.ac.in}{Link}}
\location{MDG IIT Roorkee}
Appetizer is official mobile application for IIT Roorkee aiming towards the management of mess functionalities. Features include providing mess menu, recording the presence of students, give a rebate and simplify feedback processes.
\begin{tightitemize}
\item Developed new features on the back end while maintaining existing ones.
\item Worked on Database Query Optimizing and reducing Network Traffic.
\item Implemented and tested multi-messing feature.
\item Handled the servers ensuring least service downtime.
\end{tightitemize}
\sectionspace % Some white space after the section

% Codephile

\runsubsection{Codephile}
\descript{| Back-end Head | \href{https://codephile.mdg.iitr.ac.in}{Link}}
\location{MDG IIT Roorkee}
Codephile is a social networking application for competitive coders.\\
Web application is written in Go-Lang using bee framework. It scrapes or make API requests to the platforms to show progress and statistics on users and his friends.\\
The tech stack includes Redis, Elasticache, AWS-EC2, Firebase, Nginx, MongoDB, docker \& Bee
\begin{tightitemize}
\item Headed \& mentored the back-end development and server deployment.
\end{tightitemize}
\sectionspace % Some white space after the section

\runsubsection{File Share}
\descript{| Developer | \href{https://github.com/dev-ritik/files_share}{Link}}
\location{IIT Roorkee}
File Share is a socket based file sharing application written in C++ and Sockets. The application also aims to provide a web interface to communicate to browsers via Web-Sockets.

\sectionspace % Some white space after the section

%-
%------------------------------------------------

% Project
%------------------------------------------------

\section{Achievements} 
\begin{tightitemize}
\sectionspace % Some white space after the section
\item Successfully ran Appetizer in the campus for 1 yr with the highest daily active user count of more than 3500. 
\item Our team stood 3rd in \href{https://www.hackinthenorth.com/}{Hackinthenorth} hackathon at IIIT Allahabad. 
\item Secured All India Rank 1172 in JEE Advanced - 2017 among 2, 20,000 students \& 777 in JEE Main - 2017 among 1.5 million students.


\end{tightitemize}

\sectionspace % Some white space after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}